Cross-scale integration of knowledge for predicting species ranges: a metamodeling framework

### 2015-07-27 tex/manuscript.tex
Commit changes for first revision to GEB (submitted in Apr 2015

%\usepackage[margin=1in]{geometry}

% use proper unicode fonts
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

@@

%% graphics packages
\usepackage{graphicx}
%\usepackage[nomarkers,nolists,heads]{endfloat}
\usepackage{caption}
\captionsetup{labelformat=simple}
\usepackage{booktabs}
\usepackage{multirow}

@@

%% ----------------------------------
%
%     Packages to be used for drafts and editing
%     Remove from the final manuscript
%
%% ----------------------------------
\usepackage[top=1in, left=1in, bottom=1in, right=2.0in]{geometry}
\usepackage[textsize=tiny, backgroundcolor=white, textwidth=1.8in, colorinlistoftodos=true]{todonotes} % for margin notes using \todo{}
\newcommand{\mt}[1]{\todo[color=blue!40]{\textsuperscript{MT}#1}}
\newcommand{\ib}[1]{\todo[color=red!40]{\textsuperscript{IB}#1}}
\newcommand{\fd}[1]{\todo[color=orange!40]{\textsuperscript{FD}#1}}

@@

\title{Cross-scale integration of knowledge for predicting species ranges: a metamodeling framework}
\date{}
\author[1,2,13]{Matthew V. Talluto (mtalluto@gmail.com)}
\author[1,2]{Isabelle Boulangeat (isabelle.boulangeat@gmail.com)}
\author[3]{Aitor Ameztegui (ameztegui@gmail.com)}
\author[4]{Isabelle Aubin (Isabelle.Aubin@NRCan-RNCan.gc.ca)}
\author[1,2,5]{Dominique Berteaux (Dominique\_Berteaux@uqar.ca)}
\author[1,2]{Alyssa Butler (ca.butler10@gmail.com)} 
\dg{I think we should drop her, now that she is not in science anymore}
\affil[4]{Great Lakes Forestry Centre, Canadian Forest Service, Natural Resources Canada, Sault Ste Marie, Ontario, Canada}
\affil[5]{Centre for Northern Studies, Université du Québec à Rimouski, Rimouski, Quebec, Canada}
\affil[6]{Université du Québec en Outaouais, Gatineau, Quebec, Canada}
\affil[7]{Institut des Sciences de la Forêt Tempérée (ISFORT), Ripon, Quebec, Canada}
\affil[8]{The Nature Conservancy Canada, Ottawa, Ontario, Canada}
\affil[9]{Department of Ecology and Evolutionary Biology, University of Toronto, Toronto, Ontario, Canada}
\affil[10]{Department of Mathematics, Washington State University, Vancouver, Washington, USA}
\affil[11]{Université Grenoble Alpes, Laboratoire d’Ecologie Alpine (LECA), F-38000 Grenoble, France}
\affil[12]{CNRS, Laboratoire d’Ecologie Alpine (LECA), F-38000 Grenoble, France}
\affil[13]{Author for correspondance. Address: Departament de Biologie, chimie, et geographie, 300, Allée des Ursulines, Rimouski, Quebec G5L 3A1, Canada}

@@

	\textbf{Main text word count: } 4848 %WORD_COUNT %Target 5000

@@

Current interests in forecasting potential changes to species ranges have resulted in a great diversity of approaches to species distribution modeling.
However, in general, single approaches include only a small subset of the available information about a species. 
Correlative models often predict presence or absence as a function of the environment, but ignore smaller-scale processes such as growth, fecundity, and dispersal.
Furthermore, different approaches often produce divergent predictions, with no simple method to reconcile them.
We present a flexible framework for integrating models at multiple scales using hierarchical Bayesian methods. 
Our framework uses a metamodel, estimated in a hierarchical Bayesian framework, that is constrained by both data directly applied to the metamodel and by the results of one or more sub-models.
The output of the metamodel is in the form of probabilistic estimates of species presence.
Metamodel outputs also incorporate uncertainty from both data and process error from all sub-models, and include all of the information used as input for the original scale-specific sub-models.
We illustrate our approach using theoretical and empirical examples, and demonstrate that the framework better characterizes uncertainty and can substantially reduce it when projecting beyond the range of the original data.
We conclude by discussing the application of our method and its accessibility to conservation biologists and land managers.
The framework has wide potential for use in species distribution modelling, and can drive better integration of multi-scale data into ecological decision-making.

@@

We illustrate our framework with two examples.
We begin with a hypothetical example, using simulated data, where we define the framework and demonstrate its application to multiple sources of information from different scales.
In a second example, we apply the framework to combine presence-absence information with phenological data to improve uncertainty estimates and reduce bias when predicting changes to the range of sugar maple (\emph{Acer saccharum} Marsh.), a widespread and dominant tree species from eastern North America, in response to climate change.
We provide a more formal mathematical presentation in the Appendix S1, along with complete code and data for both examples (Appendix S2).

@@

We consider data collected from a species' historical distribution, where the goal is to predict the distribution following a substantial reduction in precipitation.
For the metamodel-scale data, we simulate a relatively high-quality presence-absence dataset covering a variety of ecological conditions, which we term \(X_M\), where the subscripted \(M\) indicates that the data were collected at the same scale as the metamodel (Fig. \ref{fig:ex1_sampling}).
We desire to model the species' distribution as a function of temperature, \(T_M\), and precipitation, \(P_M\).
An initial version of the metamodel \((\theta_M)\) that has no constraints from other datasets will be referred to as the naive model.
This naive model uses a simple logistic regression to estimate the naive probability of occurrence \((\psi_N)\) as a function of second order effects of temperature and precipitation:
\dg{I dropped the 'bayesian' from this sentence because I was looking at the posterior in the following equation and only found the likelihood. It comes in the following equation.}

%-----
\begin{equation}
\begin{aligned}
	\psi_N &= f\left(\theta_M, T_M, P_M \right) \\
	&= p \left (X_M = 1 \mid \theta_M, T_M, P_M \right) \\
	&=\text{logit}^{-1}\left( \theta_M D_M \right)
\end{aligned}
\end{equation}
%-----
where \(\theta_M\) is the parameter vector of the model, \(D_M\) is the covariate matrix (i.e., \(T_M, P_M\)), and \(\text{logit}^{-1}\) is the inverse of the logit function.
We estimate parameters using a Markov Chain Monte Carlo (MCMC) method using the proportional form of Bayes' theorem:
\dg{you specify the algorithm of the sampler below, but not here}

@@

\dg{There is something wrong with the following equation, or I missed the reasonning somewhere in the last year. In any case, I tried to understand the logic from the text and haven't succeed at it. Either it needs to be fixed, or it needs to be better explained. If I don't get it, my prior tells me nobody will. This equation is central to the paper now that the maths have been put in the appendix. I was expecting to see the likelihood of X_M given the parameters theta_M.  The prior of theta_M being the posterior of the model theta_M applied to the data psi_S. The actual likelihood gives the probability of observing the prediction of the sub-model given the parameters of the sub-model. There is not integration on the conditions, it only results from the product of the probabilities.}

We accomplish model integration by treating the posterior of \(\theta_S\) as prior information about some of the parameters of \(\theta_M\) (i.e., parameters related to precipitation), expanding Equation \ref{eq:ex1_bayes} to incorporate the new information from the sub-model:
%-----
\begin{equation}
	\label{eq:ex1_integrated}
	\overbrace{p(\theta_M \mid X_M, T_M, P_M, \theta_S, \psi_S, P_S)}^\text{integrated posterior}
	\propto
	\overbrace{p\left (\psi_S \mid \theta_S,P_S \right )}^{\substack{\text{new information} \\ \text{from sub-model}}}
	\overbrace{p \left(X_M \mid \theta_M, T_M, P_M \right) p \left(\theta_M \right)}^{\substack{\text{naive metamodel} \\ \text{posterior}}}
	\overbrace{p \left(\theta_S \right)}^{\substack{\text{prior for} \\ \text{sub-model}}}	
\end{equation}
%-----
As before, the metamodel \(\theta_M\) can be used to predict probability of occurrence \((\psi_I)\).
However, these predictions now reflect the presence-absence data \(X_M\) as well as the information from \(\theta_S\), including all of the data sources used to produce this sub-model.
Finally, we note the presence of marginal distributions for both models (i.e., \(p(\theta_M)\) and \(p(\theta_S)\)).
These can be informative (e.g., incorporating further prior information or the predictions of additional sub-models), semi-informative (e.g., to provide greater weight to more informative models), or uninformative.
For purposes of this example, we used these terms to reduce the precision of the second model to reflect the uncertainty of the modeling process (due to the lack of additional mechanisms in the second model, as mentioned above).

\dg{This is a vague statement. Could you give just an extra sentence specifying how you did it, and then pointing to the Appendix?}

%==================
\begin{figure}[bt]
	\includegraphics{figs/ex1_precip.pdf}
	\caption{Comparison of the naive model, mechanistic sub-model, and the integrated model showing the probability of presence (\(\psi\)) as a function of precipitation.
	Uncertainty is represented as dashed lines, showing the limits of 90\% Bayesian credible intervals.
	The shaded region shows the calibration range for the naive model.
	(a) Naive model, using only presence-absence data. Uncertainty increases dramatically when attempting to project beyond the scope of the source data.
	(b) Mechanistic model, using observations of an experiment to infer probability of presence.
	(c) Integrated model, showing predictions that are intermediate between the two sub-models and uncertainty that is reduced compared to (a).
	}
	\label{fig:ex1_precip}
\end{figure}
%==================

@@

\dg{might worth increasing font size on the figures. And make sure it is the same for all figures.}

@@

We obtained climate variables, occurrence data, and Phenofit projections at 0.5-degree resolution for both the present and for 2080 for sugar maple, an economically and ecologically important species occurring in eastern North America \citep{Morin2009}.
These data defined the metamodel scale.
To these data, we added 4903 recorded presences and 21701 absences derived from permanent forest sample plots located in the United States and Canada (See Appendix S1 for a map of plot locations).
We reserved 1/3 of this dataset for evaluation, and used the remaining records to calibrate the models.
We constructed the naive model by using a binomial generalized linear model (GLM) to relate the presence-absence dataset to three climate variables: the number of degree days (ddeg), mean annual precipitation (an\_prcp), and the ratio of annual precipitation to potential evapotranspiration (pToPET).
These variables were selected from an initial set of 6 variables \citep[see Appendix S1 and ][for details on the climate variables]{Morin2009}.
We selected a GLM for its simplicity and interpretability because our focus was on demonstrating the framework, but more complex methods (e.g., generalized additive models) are compatible with the framework.
The parameters for the model were estimated using a Metropolis-Hastings algorithm.

@@

\subsection*{Challenges} 
Although our approach is highly flexible and can be applied in a number of situations, there are some challenges to successfully using the framework.
Data quality and availability can present a significant constraint on the number and type of models that can be implemented in our framework.
One obstacle is a lack of adequate and unbiased coverage of explanatory variables; exploratory analyses can be a significant aid in understanding how data coverage impacts resulting predictions \citep{Mckenney2002}.
Integration can solve these issues to some extent by using supplemental information (and conceptual advances) in additional sub-models where coverage is weak (e.g., Example 1, Figs. \ref{fig:ex1_precip}, \ref{fig:ex1_map}).
A strong asset of our approach is that it can be used without the full suite of data that would be required to run a fully mechanistic model. 
Given that the metamodel is correlative, it can be effectively implemented with, e.g., only presence-absence data, or, in the case where true absences are difficult to obtain, with presences and pseudo absences (provided sufficient care is used in interpreting the results of such a model).
Then any additional mechanistic data that are available will enhance predictions by constraining outputs of the metamodel.

\ib{you say in the intro that the bayesian framework allows a easy and simple scaling-up, but the scale-up is still a problem. This part about scale is still a bit unclear. Our approach do not solve the scaling-up problem.}
\fd{I fully agree with Isabellle.  Adequacy between ecological processes, scales, and meaning for upscaling the information  remain a major challenge.  It would be important here to say how this new approach helps is disentangling the difficulties listed at lines 35-37 in the introduction.}
\mt{Although scaling is always a problem, this doesn't invalidate the statement that our method makes it easier. Think of the first example. This scaling would have been very difficult to do without using Bayesian methods.}
\dg{Do agree with mt}

Determining the functions to use to express the likelihood of the sub-models given the metamodel (i.e., Eq. \ref{eq:ex1_integrated}) is a critical point.
The challenge is three fold: (i) which spatial and temporal scales (i.e. which processes), are to be considered, (ii) how to build a scale the sub-models to be consistent with the metamodels, and (iii) how error and uncertainty propagate from the sub-models to the metamodel. 
Although we argue that our proposed framework is able to easily deal with very different scales and that the Bayesian framework allows for an efficient integration of uncertainty throughout all scales considered, the building of scaling functions is an object of investigation on its own. 
It is likely that the modeling process may include multiple functions operating at different scales when taking all known processes and models into account. 
Indeed, if species distributions are a function of, e.g. population growth rate \citep{Guisan2000}, they will involve processes at the individual (e.g. competition) or cellular (e.g. photosynthesis) scales. Such very large differences in spatial scales would require more sophisticated upscaling methods than simple functions such as those we have used here. Our framework is still applicable whatever the chosen upscaling approach and is able to propagate uncertainties from sub-models to the metamodel.

\dg{I also think that there is the challenge inherent to complex systems that is overlooked to a certain extent here. Small scale processes might generate organization at higher scales. Model integration might be limited by this problem in some cases, while in others it might solve it by putting bounds on the higher-order organization. Think about the evaluation of model parameters with observations at the scale of the operating process. There are some parameter values, within the posterior distribution, that could result in non-desirable properties at the larger scale. Model integration could buffer this propagation.}

\ib{This paragraph is weired. You say that the implementation is very difficult and end the paragraph with decision, practitioners advantage.
I would end the paragraph with positive points about implementation, saying that we still can do a lot with JAGS for instance. And then start a paragraph to briefly talk about challenges in dialogue with practitionners}

@@

Finally, this approach is not just a new methodological tool but is a framework for forecasting species distributions which is fundamentally designed to make the link between modellers and pratitionners, with (1) correctly estimating uncertainties and (2) being updatable to new data or theoretical advances. A scientific approach such as presented here is particularly adapted to make a synthesis of available knowledge and provide robust species distribution forecasts based on information known as being the best of the actual scientific knowledge. It is actually able both to use large databases, valuing the efforts of data collection, and to include models based on the latest theoretical advances, which is essential to decrease the errors due to model specification \citep{Austin2007}. In addition, it would provides practionners and decision-makers with the best possible estimation of uncertainties, with direct applications to risk assessment or to guide the choice where investigating new research and accumulating new data. 
We further argue that the adaptability of our approach is particularly appropriate in our world where collected data and theoretical knowledge is changing as quickly as climate and conservation practices must be adjusted accordingly.

\fd{I am a bit feeling uncomfortable with this section.  Practionners and decision-makers don't have to use (or even fully understand (as they will never get to that level of complexity) what methods underly the predictions) the models.  They use the information known as being the best of the actual scientific knowledge.  As for climate-related variables for CC, the scientific community (as the GIEC for the CC predictions) provide the predictions on SD. The scientific community is responsible for indicating the limitations of the use of the generated information.}

\ib{I would add somewhere that this approach is not just a new methodological tool but is a framework for forecasting species distributions which is fundamentally designed to make the link between modellers and pratitionners, with (1) correctly estimating uncertainties and (2) being adaptable/updatable to new data or theoretical advances.}

>>>>

\usepackage[margin=1in]{geometry}

% use proper unicode fonts
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{fixltx2e}

@@

%% graphics packages
\usepackage{graphicx}
\usepackage[nomarkers, tablesfirst]{endfloat} % for final
\usepackage{caption}
\captionsetup{labelsep=none,textformat=empty} % for final
% \captionsetup{labelformat=simple} % for drafts
\usepackage{booktabs}
\usepackage{multirow}

@@

%% ----------------------------------
%
%     Packages to be used for drafts and editing
%     Remove from the final manuscript
%
%% ----------------------------------
%\usepackage[top=1in, left=1in, bottom=1in, right=2.0in]{geometry}
%\usepackage[textsize=tiny, backgroundcolor=white, textwidth=1.8in, colorinlistoftodos=true]{todonotes} % for margin notes using \todo{}
%\newcommand{\mt}[1]{\todo[color=blue!40]{\textsuperscript{MT}#1}}
%\newcommand{\ib}[1]{\todo[color=red!40]{\textsuperscript{IB}#1}}
%\newcommand{\fd}[1]{\todo[color=orange!40]{\textsuperscript{FD}#1}}
%\newcommand{\dg}[1]{\todo[color=green!40]{\textsuperscript{DG}#1}}

@@

\title{Cross-scale integration of knowledge for predicting species ranges: a metamodeling framework}
\date{}
\author[1,2,13]{Matthew V. Talluto (mtalluto@gmail.com)}
\author[1,2]{Isabelle Boulangeat (isabelle.boulangeat@gmail.com)}
\author[3]{Aitor Ameztegui (ameztegui@gmail.com)}
\author[4]{Isabelle Aubin (Isabelle.Aubin@NRCan-RNCan.gc.ca)}
\author[1,2,5]{Dominique Berteaux (Dominique\_Berteaux@uqar.ca)}
\author[1,2]{Alyssa Butler (ca.butler10@gmail.com)} 
\author[6,7]{Frédérik Doyon (Frederik.Doyon@uqo.ca)}
\author[8]{C. Ronnie Drever (cdrever@tnc.org)}
\author[9]{Marie-Josée Fortin (mariejosee.fortin@utoronto.ca)}
\author[1]{Tony Franceschini (Tony.Franceschini@uqar.ca)}
\author[10]{Jean Liénard (jean.lienard@gmail.com)}
\author[4]{Dan McKenney (Dan.McKenney@nrcan-rncan.gc.ca)}
\author[2,3]{Kevin A. Solarik (kevinsolarik@hotmail.com)}
\author[10]{Nikolay Strigul (nick.strigul@vancouver.wsu.edu)}
\author[11,12]{Wilfried Thuiller (wilfried.thuiller@ujf-grenoble.fr)}
\author[1,2]{Dominique Gravel (dominique\_gravel@uqar.ca)}
\affil[1]{Département de biologie, Université du Québec à Rimouski, Rimouski, Quebec, Canada}
\affil[2]{Quebec Centre for Biodiversity Science, Montreal, Quebec, Canada}
\affil[3]{Centre d'Étude de la Forêt, Département des sciences biologiques, Université du Québec à Montréal, Montreal, Quebec, Canada}
\affil[4]{Great Lakes Forestry Centre, Canadian Forest Service, Natural Resources Canada, Sault Ste Marie, Ontario, Canada}
\affil[5]{Centre for Northern Studies, Université du Québec à Rimouski, Rimouski, Quebec, Canada}
\affil[6]{Université du Québec en Outaouais, Gatineau, Quebec, Canada}
\affil[7]{Institut des Sciences de la Forêt Tempérée (ISFORT), Ripon, Quebec, Canada}
\affil[8]{The Nature Conservancy Canada, Ottawa, Ontario, Canada}
\affil[9]{Department of Ecology and Evolutionary Biology, University of Toronto, Toronto, Ontario, Canada}
\affil[10]{Department of Mathematics, Washington State University, Vancouver, Washington, USA}
\affil[11]{Université Grenoble Alpes, Laboratoire d’Ecologie Alpine (LECA), F-38000 Grenoble, France}
\affil[12]{CNRS, Laboratoire d’Ecologie Alpine (LECA), F-38000 Grenoble, France}
\affil[13]{Author for correspondance. Address: Departament de Biologie, chimie, et geographie, 300, Allée des Ursulines, Rimouski, Quebec G5L 3A1, Canada}

@@

	\textbf{Main text word count: } 4595 %WORD_COUNT %Target 5000

@@

Current interest in forecasting potential changes to species ranges have resulted in a great diversity of approaches to species distribution modeling.
However, in general, single approaches include only a small subset of the available information about a species. 
Correlative models often predict presence or absence as a function of the environment, but ignore smaller-scale processes such as growth, fecundity, and dispersal.
Furthermore, different approaches often produce divergent predictions, with no simple method to reconcile them.
We present a flexible framework for integrating models at multiple scales using hierarchical Bayesian methods. 
Our framework uses a metamodel, estimated in a hierarchical Bayesian framework, that is constrained by both data directly applied to the metamodel and by the results of one or more sub-models.
The output of the metamodel is in the form of probabilistic estimates of species presence.
Metamodel outputs also incorporate uncertainty from both data and process error from all sub-models, and include all of the information used as input for the original scale-specific sub-models.
We illustrate our approach using theoretical and empirical examples, and demonstrate that the framework better characterizes uncertainty and can substantially reduce it when projecting beyond the range of the original data.
We conclude by discussing the application of our method and its accessibility to conservation biologists and land managers.
The framework has wide potential for use in species distribution modelling, and can drive better integration of multi-scale data into ecological decision-making.

@@

We illustrate our framework with two examples.
We begin with a hypothetical example, using simulated data, where we define the framework and demonstrate its application to multiple sources of information from different scales.
In a second example, we apply the framework to combine presence-absence information with phenological data to improve uncertainty estimates and reduce bias when predicting changes to the range of sugar maple (\emph{Acer saccharum} Marsh.), a widespread and dominant tree species from eastern North America, in response to climate change.
We provide a more formal mathematical presentation in Appendix S1, along with complete code and data for both examples (Appendix S2).

@@

We consider data collected from a species' historical distribution, where the goal is to predict the distribution following a substantial reduction in precipitation.
For the metamodel-scale data, we simulate a relatively high-quality presence-absence dataset covering a variety of ecological conditions, which we term \(X_M\), where the subscripted \(M\) indicates that the data were collected at the same scale as the metamodel (Fig. \ref{fig:ex1_sampling}).
We desire to model the species' distribution as a function of temperature, \(T_M\), and precipitation, \(P_M\).
An initial version of the metamodel \((\theta_M)\) that has no constraints from other datasets will be referred to as the naive model.
This naive model uses a simple logistic regression to estimate the naive probability of occurrence \((\psi_N)\) as a function of second order effects of temperature and precipitation:

%-----
\begin{equation}
\begin{aligned}
	\psi_N &= f\left(\theta_M, T_M, P_M \right) \\
	&= p \left (X_M = 1 \mid \theta_M, T_M, P_M \right) \\
	&=\text{logit}^{-1}\left( \theta_M D_M \right)
\end{aligned}
\end{equation}
%-----
where \(\theta_M\) is the parameter vector of the model, \(D_M\) is the covariate matrix (i.e., \(T_M, P_M\)), and \(\text{logit}^{-1}\) is the inverse of the logit function.
We estimate parameters using a Metropolis-Hastings algorithm within a Markov Chain Monte Carlo (MCMC) method using the proportional form of Bayes' theorem:

@@

We accomplish model integration by treating the \(\psi_S\), the posterior predictions of the submodel\(\theta_S\), as prior information about some of the parameters of \(\theta_M\) (i.e., parameters related to precipitation), expanding Equation \ref{eq:ex1_bayes} to incorporate the new information from the sub-model:
%-----
\begin{equation}
	\label{eq:ex1_integrated}
	\overbrace{p(\theta_M \mid X_M, T_M, P_M, \theta_S, \psi_S)}^\text{integrated posterior}
	\propto
	\overbrace{p\left (\psi_S \mid \theta_M,P_M \right )}^{\substack{\text{new information} \\ \text{from sub-model}}}
	\overbrace{p \left(X_M \mid \theta_M, T_M, P_M \right) p \left(\theta_M \right)}^{\substack{\text{naive metamodel} \\ \text{posterior}}}
	\overbrace{p \left(\theta_S \right)}^{\substack{\text{prior for} \\ \text{sub-model}}}	
\end{equation}
%-----
%\dg{There is something wrong with the following equation, or I missed the reasonning somewhere in the last year. In any case, I tried to understand the logic from the text and haven't succeed at it. Either it needs to be fixed, or it needs to be better explained. If I don't get it, my prior tells me nobody will. This equation is central to the paper now that the maths have been put in the appendix. I was expecting to see the likelihood of X\_M given the parameters theta\_M.  The prior of theta\_M being the posterior of the model theta\_M applied to the data psi\_S. The actual likelihood gives the probability of observing the prediction of the sub-model given the parameters of the sub-model. There is not integration on the conditions, it only results from the product of the probabilities.}
As before, the metamodel \(\theta_M\) can be used to predict probability of occurrence \((\psi_I)\).
However, these predictions now reflect the presence-absence data \(X_M\) as well as the information from \(\theta_S\), including all of the data sources used to produce this sub-model.
Finally, we note the presence of marginal distributions for both models (i.e., \(p(\theta_M)\) and \(p(\theta_S)\)).
These can be informative (e.g., incorporating further prior information or the predictions of additional sub-models), semi-informative (e.g., to provide greater weight to more informative models), or uninformative.
For purposes of this example, we applied prior weights of 20 and 1 to the correlative and mechanistic models, respectively, reflecting the increased generality and much larger sample size of the correlative data.
This procedure has the effect of increasing the variance of the model and prevents biasing the parameter estimation in favor of the mechanistic model.

%==================
\begin{figure}[bt]
	\includegraphics{figs/ex1_precip.pdf}
	\caption{Comparison of the naive model, mechanistic sub-model, and the integrated model showing the probability of presence $(\psi)$ as a function of precipitation.
	Uncertainty is represented as dashed lines, showing the limits of 90\% Bayesian credible intervals.
	The shaded region shows the calibration range for the naive model.
	(a) Naive model, using only presence-absence data. Uncertainty increases dramatically when attempting to project beyond the scope of the source data.
	(b) Mechanistic model, using observations of an experiment to infer probability of presence.
	(c) Integrated model, showing predictions that are intermediate between the two sub-models and uncertainty that is reduced compared to (a).
	}
	\label{fig:ex1_precip}
\end{figure}
%==================

@@

@@

We obtained climate variables, occurrence data, and Phenofit projections at 0.5-degree resolution for both the present and for 2080 for sugar maple, an economically and ecologically important species occurring in eastern North America \citep{Morin2009}.
These data defined the metamodel scale.
To these data, we added 4903 recorded presences and 21701 absences derived from permanent forest sample plots located in the United States and Canada (See Appendix S1 for a map of plot locations).
We reserved 1/3 of this dataset for evaluation, and used the remaining records to calibrate the models.
We constructed the naive model by using a binomial generalized linear model (GLM) to relate the presence-absence dataset to three climate variables: the number of degree days (ddeg), mean annual precipitation (an\_prcp), and the ratio of annual precipitation to potential evapotranspiration (pToPET).
These variables were selected from an initial set of 6 variables \citep[see Appendix S1 and ][for details on the climate variables]{Morin2009}.
We selected a GLM for its simplicity and interpretability because our focus was on demonstrating the framework, but more complex methods (e.g., generalized additive models) are compatible with the framework.

@@

\subsection*{Challenges} 
Although our approach is highly flexible and can be applied in a number of situations, there are some challenges to successfully using the framework.
Data quality and availability can present a significant constraint on the number and type of models that can be implemented in our framework.
One obstacle is a lack of adequate and unbiased coverage of explanatory variables; exploratory analyses can be a significant aid in understanding how data coverage impacts resulting predictions \citep{Mckenney2002}.
Integration can solve these issues to some extent by using supplemental information (and conceptual advances) in additional sub-models where coverage is weak (e.g., Example 1, Figs. \ref{fig:ex1_precip}, \ref{fig:ex1_map}).
A strength of our approach is that it can be used without the full suite of data that would be required to run a fully mechanistic model. 
Given that the metamodel is correlative, it can be effectively implemented with, e.g., only presence-absence data, or, in the case where true absences are difficult to obtain, with presences and pseudo absences (provided sufficient care is used in interpreting the results of such a model).
Then any additional mechanistic data that are available will enhance predictions by constraining outputs of the metamodel.

Determining the functions to use to express the likelihood of the sub-models given the metamodel (i.e., Eq. \ref{eq:ex1_integrated}) is a critical point.
The challenge is three fold: (1) which spatial and temporal scales (i.e. which processes), are to be considered, (2) how to build a scale the sub-models to be consistent with the metamodels, and (3) how error and uncertainty propagate from the sub-models to the metamodel. 
Although we argue that our proposed framework is able to easily deal with very different scales and that the Bayesian framework allows for an efficient integration of uncertainty throughout all scales considered, the building of scaling functions is an object of investigation on its own. 
It is likely that the modeling process may include multiple functions operating at different scales when taking all known processes and models into account. 
Indeed, if species distributions are a function of, e.g. population growth rate \citep{Guisan2000}, they will involve processes at the individual (e.g. competition) or cellular (e.g. photosynthesis) scales. Such very large differences in spatial scales would require more sophisticated upscaling methods than simple functions such as those we have used here. Our framework is still applicable whatever the chosen upscaling approach and is able to propagate uncertainties from sub-models to the metamodel.

@@

Finally, this approach is not just a new methodological tool but is a framework for forecasting species distributions which is fundamentally designed to make the link between modelers and practitioners while correctly estimating uncertainties and being updatable with new data and theoretical advances. 
A scientific approach such as presented here is particularly adapted to make a synthesis of available information and provide robust species distribution forecasts based on information known to be the best available scientific knowledge. 
It can incorporate large databases, valuing the efforts of data collection, and include models based on the latest theoretical advances, which is essential to decrease errors due to model specification \citep{Austin2007}. 
In addition, it provides practitioners and decision-makers with the best possible estimation of uncertainties, with direct applications to risk assessment or to guide the choice where investigating new research and accumulating new data. 
Finally, we argue that the adaptability of our approach is particularly appropriate in a world where collected data and theoretical knowledge is changing as quickly as climate and conservation practices must be adjusted accordingly.
